\section{Simulation of Environmental Wireless Sensor Networks (E-WSN)}
	
	\subsection{System components and layout}
	
	To define our simulation clearly we will base it on a realistic deployment scenario as covered by Gomez et al \cite{Gomez} and others \cite{Jha2016, Avram}. We will use a UAV to deploy a large number of sensors over a large and remote geographical area, leading to a relatively ad-hoc, randomised placement of devices. They will use solar power cells to maintain enough energy to power themselves over a number of years, making clear the requirement for low power usage. Noting that the transceiver is the significant power drain on these sensors we can see that reducing its utilisation will be one of the keys to managing energy usage. We will design our sensors to use \textit{Wake Up Radio} (WUR) and aim our agent deployment strategy towards minimising its use and range. As mentioned, the other main driver of the way we use the agents to control the sensors will be the resilience and adaptivity of the system over long periods of time, with no human intervention possible.  We summarise the key target criteria for our E-WSN and therefore our agent simulation in Table \ref {table:real_world_systems_criteria} 
	\begin{table}
		\begin{tabular}{p{0.1\textwidth}p{0.4\textwidth} p{0.4\textwidth}}
			\hline
			\textbf{Criteria} & \textbf{Description} & \textbf{Agent-system element} \\
			\hline
			Low energy use & Remote location devices can only recover energy slowly through solar panel charging &  Use link energy consumption values to optimse learning towards efficient neighbourhoods \\
			Resilience to node failure & Remote and dangerous locations mean human maintenance is either impossible, expensive, or otherwise restricted & Neighbourhood link adaptation algorithms \\	
			Power consumption distribution & Devices have independent energy recovery mechanisms and would be overwhelmed with too much load. Although other agents would then take over this leads to unstable networks & Link energy consumption value rate accumulation for agents can be used to shape rewards to drive agent local neighbourhood adaptation away from overloaded agents  \\ 
			\hline
		\end{tabular}
		\caption{Key criteria for E-WSN systems}
		\label{table:real_world_systems_criteria}
	\end{table}
	

	\subsection{Assumptions}
	We make the following assumptions and simplifications.
	\begin{itemize}{
			\item Node deployment is randomly distributed across the grid following the uniform distribution or a radial normal distribution.
			\item Energy harvesting works continuously at constant rate. This assumes consistent solar exposure and limits the simulation to daytime.
			\item Permanent node failure is based on the total energy consumption of that node over time, as a proxy for wear. Node failure is therefore chosen using a Boltzmann distribution\footnote{Where the Boltzmann distribution is defined as $\functionBoltzmannEnergy{}{}$} over the lifetime energy usage of an agent.
			\item Temporary loss of availability of nodes is random and at a constant rate.
		}
	\end{itemize}
	
	
	
	
	\begin{definition}[Energy]
		XXX
	\end{definition}
	
	